---
title: "Exercise #1"
author: "Yazmin Baptiste"
date: "November 2, 2023"
output: html_document
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE) 
library("dplyr")
library("tidyverse")
```

## Documentation for `multiply_numeric`

The multiply numeric function is useful if you want to multiply all numeric
columns in your dataset by a certain number. First, it identifies if a column
is numeric, then conducts the transformations based on the number you 
selected. An example of how this works is below:

```{r function, include = FALSE}
multiply_numeric<- function(data, multiplier){
  transformed_df <- data %>%
    mutate_if(is.numeric, ~ . * multiplier)
  
  return(transformed_df)
}
```

Here is a preview of what the dataset looks like before the transformation:
```{r get data}
data("relig_income")
head(relig_income)
```

Here is how that same dataset looks after we use the function to multiply
every numeric column by 2
```{r}
head(multiply_numeric(relig_income, 2))
```
And here is how it looks using the same function but with .5:
```{r}
head(multiply_numeric(relig_income, .5))
```

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
```